Are Delayed Issues Harder to Resolve? Revisiting Cost-to-Fix of Defects throughout the Lifecycle

### 2016-09-12 lucas.tex
Updates from ShareLaTeX

Our survey collected data on software engineers' views of commonly held software engineering ``laws''.
One of the laws questioned is the a specific form of our delayed issue effect:  ``requirements errors are the most expensive to fix when found during production but the cheapest to fix early in development'' (from Glass~\cite{glass02} p.71 who references Boehm \& Basili~\cite{boehm01}). We abbreviate this law as RqtsErr
(and is
illustrated in \fig{b81}).

(Technical aside: we    ask them  RqtsErr  since this issue typically needs no supportive explanatory
text. On the other hand, if we had asked them about our more general term ``delayed issue
effect'', we would have had to burden our respondents with extra explanations).

The survey was conducted in two phases using Amazon's Mechanical Turk. The first phase was conducted only with professional software engineers solicited through the Mechanical Turk,
Professional software engineers were required to complete a pretest to verify their status as a professional or open source software developer and to confirm their knowledge of basic software engineering terminology and technology. The  second survey was conducted Program Committee members of the ESEC/FSE 2015 and ICSE 2014  conferences solicited via email.

@@

In order to baseline the participant's answers, participants were presented with the RqtsErr law and others. For the purposes
of this paper, the nature of the other laws other than RqtsErr are not relevant-- we
only added them in as a way to calibrate responses to the RqtsErr question. All laws were drawn from \cite{glass02} and \cite{endres03}. 
The PC member survey contained an additional question on ``In general, the longer errors are in the system (requirements errors, design errors, coding errors, etc.), the more expensive they are to fix'' (the Delayed Issue Effect, for short). Responses were recorded using the agreement question Likert scale.

@@

Both  practitioners and researchers  strongly believed in RqtsErr (in both sets of responses, RqtsErr, received  scores higher than most
other laws. Further, in the case of practitioners, this law was rated
as the single most believed effect. 
%The free response texts, most participants agreed that addressing errors %%late may mean system redesign unless the system and the affected %equirement are simple/trivial. Further, any changes to the production %ystem have additional complexity (compared to changes while system in %evelopment) due to users, data existence, and architecture dependencies. 
Caveat: in the free reponse texts, we note that the researchers who disagreed with the law generally asserted that requirements change can be expensive, but that depends on the process used (e.g., agile vs. waterfall) and the adaptability of the system architecture.

>>>>

Our survey collected data on software engineers' views of commonly held software engineering ``laws''.
One of the laws questioned is a specific form of our delayed issue effect:  ``requirements errors are the most expensive to fix when found during production but the cheapest to fix early in development'' (from Glass~\cite{glass02} p.71 who references Boehm \& Basili~\cite{boehm01}). We abbreviate this law (illustrated in \fig{b81}) as RqtsErr.

(Technical aside: we use the RqtsErr formulation since this issue typically needs no supportive explanatory
text. If we had asked respondents about our more general term ``delayed issue
effect'', we would have had to burden our respondents with extra explanations).

The survey was conducted in two phases using Amazon's Mechanical Turk. The first phase was conducted only with professional software engineers solicited through the Mechanical Turk;
participants were required to complete a pretest to verify their status as a professional or open source software developer and to confirm their knowledge of basic software engineering terminology and technology. The  second survey was conducted with Program Committee members of the ESEC/FSE 2015 and ICSE 2014  conferences solicited via email.

@@

In order to baseline the participant's answers, participants were presented with the RqtsErr law and others. For the purposes
of this paper, the nature of the other laws other than RqtsErr are not relevant-- we
only added them in as a way to calibrate responses to the RqtsErr question. All laws were drawn from \cite{glass02} and \cite{endres03}. 
The PC member survey contained an additional question on ``In general, the longer errors are in the system (requirements errors, design errors, coding errors, etc.), the more expensive they are to fix'' (the Delayed Issue Effect). Responses were recorded using the agreement question Likert scale.

@@

Both  practitioners and researchers  strongly believed in RqtsErr: In both sets of responses, RqtsErr received  scores higher than most
other laws. Further, in the case of practitioners, this law was rated
as the single most believed effect. 
%The free response texts, most participants agreed that addressing errors %%late may mean system redesign unless the system and the affected %equirement are simple/trivial. Further, any changes to the production %ystem have additional complexity (compared to changes while system in %evelopment) due to users, data existence, and architecture dependencies. 
Caveat: in the free reponse texts, we note that the researchers who disagreed with the law generally asserted that requirements change can be expensive, but that the effect depends on the process used (e.g., agile vs. waterfall) and the adaptability of the system architecture.
